Think deep for reef resilience

### 2025-09-13 paper/paper_draft.qmd
Render variables with math notation

To assess the impact of reef connectivity on modelled outcomes we summarise incoming
connectivity (weighted incoming connectivity), outgoing connectivity (outgoing connection
strength), the ratio of source-to-sink connectivity, and larval retention probability for
each reef. Weighted incoming connectivity is calculated by summing the product of each
connection strength incoming to a target reef and the mean timeseries absolute coral cover
(km^2^) of each matching source reef. This metric provides an approximation of overall
larval flow into a reef, with high values indicating the target reef is supplied high
volumes of larvae via strong connections and low values indicating the target reef has weak
(or no) incoming connections or is supplied by small source populations. A limitation of
weighted incoming connectivity is it does not incorporate the proportion of the source
reef's population that is reproducing and producing larvae, instead taking the total coral
cover area as an indicator of larval productivity. Outgoing connection strength is
calculated as the sum of all outgoing transition probabilities from a target reef. Outgoing
connection strength has a theoretical maximum of one (all larvae reach settlement on sink
reefs), however the large size of the GBR combined with larval mortality considerations
result in outgoing connection strength values much lower than one. The ratio of
source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
outgoing larval flow relative to it's incoming larval flow. This is calculated as:
$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where S represents the sum of connectivity pobabilities, N
represents the number of connections, O denotes outgoing connectivity from the target reef
and I denotes incoming connectivity to the target reef. If a reef has no incoming
connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,
do not directly represent the larval supply gained as the breeding populations from which
connections are coming from are not represented. A source-to-sink ratio greater than 1 (a
value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
larval flow. Reef larval retention probability indicates the proportion of spawned larvae
from a target reef that remain to settlement.

>>>>

To assess the impact of reef connectivity on modelled outcomes we summarise incoming
connectivity (weighted incoming connectivity), outgoing connectivity (outgoing connection
strength), the ratio of source-to-sink connectivity, and larval retention probability for
each reef. Weighted incoming connectivity is calculated by summing the product of each
connection strength incoming to a target reef and the mean timeseries absolute coral cover
(km^2^) of each matching source reef. This metric provides an approximation of overall
larval flow into a reef, with high values indicating the target reef is supplied high
volumes of larvae via strong connections and low values indicating the target reef has weak
(or no) incoming connections or is supplied by small source populations. A limitation of
weighted incoming connectivity is it does not incorporate the proportion of the source
reef's population that is reproducing and producing larvae, instead taking the total coral
cover area as an indicator of larval productivity. Outgoing connection strength is
calculated as the sum of all outgoing transition probabilities from a target reef. Outgoing
connection strength has a theoretical maximum of one (all larvae reach settlement on sink
reefs), however the large size of the GBR combined with larval mortality considerations
result in outgoing connection strength values much lower than one. The ratio of
source-to-sink connectivity ($O:I$) for a target reef represents the strength of the reef's
outgoing larval flow relative to it's incoming larval flow. This is calculated as:
$O:I = \frac{S_O/N_O}{S_I/N_I}$. Where $S$ represents the sum of connectivity probabilities,
$N$ represents the number of connections, $O$ denotes outgoing connectivity from the target
reef and $I$ denotes incoming connectivity to the target reef. If a reef has no incoming
connections, the $O:I$ equals the $S_O/N_O$ value. Incoming connections in this calculation,
do not directly represent the larval supply gained as the breeding populations from which
connections are coming from are not represented. A source-to-sink ratio greater than 1 (a
value greater than 0 on a log scale) indicates a reef has greater outgoing than incoming
larval flow. Reef larval retention probability indicates the proportion of spawned larvae
from a target reef that remain to settlement.
